Self-assembly of colloid-cholesteric composites provides a possible route to switchable optical materials

### 2014-03-05 papers/2012-sandwich/CholColloids.tex
Correct spelling
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2328 40876441-3496-0410-a613-a2fca35b2ae2

\noindent
When spherical colloidal particles are mixed into a nematic liquid crystal, 
they disrupt the orientational order in the fluid and create defects (disclination lines) in the nematic close to their surfaces. To minimize the free energy cost, it is generally advantageous for defects to be shared:
therefore the colloidal particles have a generic tendency to aggregate. Such aggregates may further 
self-assemble into lines~\cite{wiresmiha}, 2D crystals~\cite{zumer}, 
planar structures~\cite{tanaka}, or 3D amorphous glasses~\cite{tiffany}.
Besides being of fundamental interest to materials science, these
structures may have tunable elastic and optical properties~\cite{stark}. Hence 
they offer exciting prospects for applications as biosensors~\cite{abbott}, or
as new devices~\cite{colloiddevice,tanakanatmat}.

@@

\centerline{\includegraphics[width=\textwidth]{text-fig1.jpg}}
\caption{\textbf{Bulk blue phase structures.} Snapshots of the states
obtained after dispersing
a suspension of colloidal nanoparticles within a cholesteric liquid
crystal in the BPI-forming region. (A-D) correspond to the case
of a dispersion of particles in a pre-equilibrated BPI phase;
(E-H) are obtained by dispersing colloids in an isotropic
phase and then quenching into the range where BPI is stable, leading to formation of an amorphous, BPIII-like, disclination network.
Structures correspond
to (A,E) $w=0.23$ and $\phi=1\%$;
(B,F) $w=0.23$ and $\phi=5\%$; 
(C,G) $w=2.3$ and $\phi=1\%$; and
(D,H) $w=2.3$ and $\phi=5\%$.
The anchoring of the director field to the colloidal surface is normal.
[For the full parameter list used to generate Figs.~1-3 see Supplementary
Information.] For clarity, only a portion of the simulation box is shown
\textcolor{red}{its extent being $\simeq 28R$}
(one eighth of the total volume);
the full structures are shown in
Supplementary Figs.~2 and~3.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{col_disc_x_run1267.png}
\includegraphics[width=0.45\textwidth]{sq_x_run1267.png}\\
\includegraphics[width=0.5\textwidth]{col_disc_x_run1341.png}
\includegraphics[width=0.45\textwidth]{sq_x_run1341.png}
\end{center}
\caption{\textbf{Structure in electric field.}
Steady states obtained when a dispersion of colloids is inserted
into a thermodynamically stable bulk BPIII with and without applied
external electric field. Panel A shows the situation in zero field, and panel
C the situation when the applied field is in the $x$-direction
(perpendicular to the plane of the paper). Panels B and D show one
plane of the three-dimensional structure factor $S(\mathbf{k})$ computed
from the positions of the particles, with wavevector $k_x = 0$, corresponding
to A and C respectively. With field, the disclinations form a honeycomb
pattern with hexagonal ordering perpendicular to the field direction;
this is reflected in the structure factor.
Simulations use weakly anchoring particles $w=0.23$, and a volume
fraction of $\phi=5\%$ (see Supplementary Information for full list of
parameters).
\textcolor{red}{The full simulation with a box size of $\simeq 56R$ is shown.}}
\end{figure}

>>>>

\noindent
When spherical colloidal particles are mixed into a nematic liquid crystal, 
they disrupt the orientational order in the fluid and create defects (disclination lines) in the nematic close to their surfaces. To minimise the free energy cost, it is generally advantageous for defects to be shared:
therefore the colloidal particles have a generic tendency to aggregate. Such aggregates may further 
self-assemble into lines~\cite{wiresmiha}, 2D crystals~\cite{zumer}, 
planar structures~\cite{tanaka}, or 3D amorphous glasses~\cite{tiffany}.
Besides being of fundamental interest to materials science, these
structures may have tunable elastic and optical properties~\cite{stark}. Hence 
they offer exciting prospects for applications as biosensors~\cite{abbott}, or
as new devices~\cite{colloiddevice,tanakanatmat}.

@@

\centerline{\includegraphics[width=\textwidth]{text-fig1.jpg}}
\caption{\textbf{Bulk blue phase structures.} Snapshots of the states
obtained after dispersing
a suspension of colloidal nanoparticles within a cholesteric liquid
crystal in the BPI-forming region. (A-D) correspond to the case
of a dispersion of particles in a pre-equilibrated BPI phase;
(E-H) are obtained by dispersing colloids in an isotropic
phase and then quenching into the range where BPI is stable, leading to formation of an amorphous, BPIII-like, disclination network.
Structures correspond
to (A,E) $w=0.23$ and $\phi=1\%$;
(B,F) $w=0.23$ and $\phi=5\%$; 
(C,G) $w=2.3$ and $\phi=1\%$; and
(D,H) $w=2.3$ and $\phi=5\%$.
The anchoring of the director field to the colloidal surface is normal.
[For the full parameter list used to generate Figs.~1-3 see Supplementary
Information.] For clarity, only a portion of the simulation box is shown
\textcolor{red}{its linear extent being $\simeq 28R$}
(one eighth of the total volume);
the full structures are shown in
Supplementary Figs.~2 and~3.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.48\textwidth]{col_disc_x_run1267.png}
\includegraphics[width=0.43\textwidth]{sq_x_run1267.png}\\
\includegraphics[width=0.48\textwidth]{col_disc_x_run1341.png}
\includegraphics[width=0.43\textwidth]{sq_x_run1341.png}
\end{center}
\caption{\textbf{Structure in electric field.}
Steady states obtained when a dispersion of colloids is inserted
into a thermodynamically stable bulk BPIII with and without applied
external electric field. Panel A shows the situation in zero field, and panel
C the situation when the applied field is in the $x$-direction
(perpendicular to the plane of the paper). Panels B and D show one
plane of the three-dimensional structure factor $S(\mathbf{k})$ computed
from the positions of the particles, with wavevector $k_x = 0$, corresponding
to A and C respectively. With field, the disclinations form a honeycomb
pattern with hexagonal ordering perpendicular to the field direction;
this is reflected in the structure factor.
Simulations use weakly anchoring particles $w=0.23$, and a volume
fraction of $\phi=5\%$ (see Supplementary Information for full list of
parameters).
\textcolor{red}{The full simulation with a box size of $\simeq 56R$ is shown.}}
\end{figure}
